\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{microtype}
\hypersetup{colorlinks=true,urlcolor=blue}
\setlength{\parindent}{0pt}
\usepackage[absolute]{textpos}
  \TPGrid{16}{16}
\usepackage[top=2\TPVertModule, bottom=2\TPVertModule, left=3\TPHorizModule, right=2\TPHorizModule]{geometry}
\usepackage{fancyhdr}
  \pagestyle{fancy}
  \renewcommand{\headrulewidth}{0pt}
  \fancyhf{}
  \rhead{}
  \rfoot{\small Page~\thepage}

\begin{document}

\begin{document}

\section*{Artemiy Rodionov}

\href{mailto:wertins71@gmail.com}{wertins71@gmail.com} / \href{https://t.me/artemiy312}{telegram.me/artemiy312} \\
\href{https://stackoverflow.com/users/6800156}{StackOverflow} /
\href{https://github.com/artemiy312}{GitHub} /
\href{https://gitlab.com/artemiy312}{GitLab} \\

\textbf{Software developer} with experience in complex projects and
distributed software development teams. Hands-on Python and JavaScript programmer.
Fond of skiing and painting. Russia, Saint-Petersburg, UTC +3.

\subsection*{Projects}

\textbf{2018}. \href{https://github.com/fidals/cryptotrader}{Cryptocurrency trading bot}
I developed a unified API for trading exchanges, a trades dashboard and algorithms.
Async Event-Driven architecture; PyTest unit and integration tests; TimescaleDB, Redis; Drone CI, Docker, Sentry.\\

\textbf{2017}. \href{https://start.ru/}{Streaming media platform}
I worked mostly on video transcoding services, but also on REST APIs and
admin dashboard. Sync/Async REST microservices; MongoDB, Redis, RabbitMQ;
Gitlab CI, Docker, Sentry; Yandextank; ffmpeg to handle media containers. \\

\textbf{2016}. \href{https://github.com/fidals/stroyprombeton}{Stroyprombeton}
I worked on online stores \href{https://github.com/fidals/shopelectro}{Shopelectro}
and \href{https://github.com/fidals/stroyprombeton}{Stroyprombeton} based on our own
e-commerce Django packages. Python, JavaScript ES6; Django, jQuery;
Automated Selenium integration tests; PostgreSQL, Redis, RabbitMQ;
Drone CI, Docker, Sentry.\\

\textbf{2016}. \href{https://github.com/fidals/shopelectro}{Shopelectro}
I worked on online stores \href{https://github.com/fidals/shopelectro}{Shopelectro}
and \href{https://github.com/fidals/stroyprombeton}{Stroyprombeton} based on our own
e-commerce Django packages. Python, JavaScript ES6; Django, jQuery;
Automated Selenium integration tests; PostgreSQL, Redis, RabbitMQ;
Drone CI, Docker, Sentry.

\subsection*{Career}

juny 2016 - present: Python developer @ \href{https://github.com/fidals/}{Fidals}

Fidals is a distributed software development team. We develop back-end services in Python.


\end{document}
